### 2016-10-30 paper/evaluation.tex
Updated setup section and added more comments/reminders

We evaluated the characteristics of regression tests in
open-source development from a sample set of Java projects
from Github. We are interested in understanding the preva-
lence of long test runs, the main source of cost, and how
often developers explore parallelism to improve execution
performance. We pose the following research questions:

@@

To run our experiments we used a Core i7-4790 (3.60GHz) Intel
processor machine with 8 virtual CPUs (4 cores with 2 native threads
each) and 16GB of memory, running on Ubuntu 14.04 LTS (64-bit
version). \Fix{add Vagrantfile with software settings} All the source
artifacts, including supporting scripts (\eg, the script that test
subjects and generates the raw data), and the full list of projects
are publicly available at \Fix{...}.

>>>>

We evaluated the characteristics of regression tests in open-source
development from a sample set of Java projects from
Github\Jbc{Remember to update the previous sentence after updating the
subject section}. We are interested in understanding the preva- lence
of long test runs, the main source of cost, and how often developers
explore parallelism to improve execution performance. We pose the
following research questions:

@@

To run our experiments we used a Core i7-4790 (3.60 GHz) Intel
processor machine with 8 virtual CPUs (4 cores with 2 native threads
each) and 16GB of memory, running on Ubuntu 14.04 LTS Trusty Tahr
(64-bit version). We provided a \emph{Vagrantfile} to emulate our
hardware and software setup and dependency settings for replication.
All the source artifacts, including supporting scripts (\eg, the
script that test subjects and generates the raw data), and the full
list of projects are publicly available at \Fix{create gh-pages}.
